### 2022-05-25 main/chapter_2ljets.tex
edit leptons, add isolation paragraph

Reconstructed lepton objects feature momenta, charges, and flavours.
Each is included only if it satisfies certain kinematic and
is identified with certain `quality' requirements.

Muons are identified by fitting tracks to hits in the inner tracker and muon
spectrometer, and their quality requirements use goodness-of-fit metrics of
those fits along with low level details of detector interactions, to primarily
to reduce backgrounds from non-prompt muons from hadronic
decays~\cite{atlas_muon_quality_MUON_2018_03}.

Electron identification combines data from the inner tracker and
calorimeters. Electron quality criteria use numerous features of detector
interactions, track fitting metrics, matching of those tracks to calorimeters,
calorimeter shower shapes, and leakage into the hadronic calorimeter to reduce
backgrounds from photons, hadrons, and non-prompt electrons from hadronic
decays~\cite{atlas_egamma_quality_EGAM_2018_01}.

>>>>

Reconstructed lepton objects feature momenta, charges, and flavours.
Each is included only if it satisfies certain kinematic and
is identified with `quality' criteria.
For both electron and muons, these criteria are standardized with labels
`loose', `medium', and `tight'.
These are nested, in the sense that tight implies medium,
and medium implies loose.
Other, more specialized, criteria exist, but they are not relevant $\twoljets$.

Muons are identified by fitting tracks to hits in the inner tracker and muon
spectrometer.
Their quality criteria use goodness-of-fit metrics from those fits, along with
low-level details of detector interactions.
Tighter requirements primarily act to to reduce from non-prompt backgrounds,
which are muons from hadronic decays~\cite{atlas_muon_quality_MUON_2018_03}.

Electron identification combines data from the inner tracker and
calorimeters.
Electron quality criteria use numerous features of detector
interactions, track fitting metrics, the matching of tracks to calorimeter
clusters, calorimeter shower shapes, and leakage into the hadronic calorimeter.
Tighter requirements reduce backgrounds, which include misidentified objects
--- photons and hadrons --- as well as non-prompt electrons from hadronic
decays~\cite{atlas_egamma_quality_EGAM_2018_01}.

Isolation of leptons from nearby hadronic activity is another feature which
can be used to reduce misidentification rates.
Standard isolation definitions exist for both electrons and muons in a similar
structure to the quality criteria.
